Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s03_drp.tex
Major restructuring of DRP section.

@@

% \begin{figure*}\centering
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (1,1) {$R_j$};
%     \node[v] (v2) at (3,1) {$R_k$};
%     \node[v] (v3) at (2,2) {$D$};
%     \node[v] (v4) at (2,3.3) {$R_i$};

%     \tedge{v1}{v3}{solid}{}{above};
%     \tedge{v2}{v3}{solid}{}{above};
%     \tedge{v3}{v4}{solid}{}{right};
% \end{tikzpicture}
% \ldots with weights \ldots
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (1,1) {y};
%     \node[v] (v2) at (3,1) {z};
%     \node[v] (v3) at (2,2) {k};
%     \node[v] (v4) at (2,3.3) {x};

%     \tedge{v1}{v3}{solid}{y}{above};
%     \tedge{v2}{v3}{solid}{z}{above};
%     \tedge{v3}{v4}{solid}{x}{right};

%     % \draw (3.3,2.5) circle (1.9cm);
%     % \draw (.7,2.5) circle (1.9cm);
%     % \draw (2,.5) circle (1.9cm);
% \end{tikzpicture}
% \\
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (0,  0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxy};
%     \node[v] (v3) at ( 1,-1) {kyz};
%     \node[v] (v4) at (-2,-2) {kx};
%     \node[v] (v5) at ( 0,-2) {ky};
%     \node[v] (v6) at ( 2,-2) {kz};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v3}{solid}{}{};
%     \tedge{v2}{v4}{solid}{}{};
%     \tedge{v2}{v5}{solid}{}{};
%     \tedge{v3}{v5}{solid}{}{};
%     \tedge{v3}{v6}{solid}{}{};
% \end{tikzpicture}
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (0,  0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxy};
%     \node[v] (v3) at ( 1,-1) {kxz};
%     \node[v] (v4) at (-2,-2) {kx};
%     \node[v] (v5) at ( 0,-2) {ky};
%     \node[v] (v6) at ( 2,-2) {kz};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v3}{solid}{}{};
%     \tedge{v2}{v4}{solid}{}{};
%     \tedge{v2}{v5}{solid}{}{};
%     \tedge{v3}{v4}{solid}{}{};
%     \tedge{v3}{v6}{solid}{}{};
% \end{tikzpicture}
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (0,  0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxz};
%     \node[v] (v3) at ( 1,-1) {kyz};
%     \node[v] (v4) at (-2,-2) {kx};
%     \node[v] (v5) at ( 0,-2) {ky};
%     \node[v] (v6) at ( 2,-2) {kz};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v3}{solid}{}{};
%     \tedge{v2}{v4}{solid}{}{};
%     \tedge{v2}{v6}{solid}{}{};
%     \tedge{v3}{v5}{solid}{}{};
%     \tedge{v3}{v6}{solid}{}{};
% \end{tikzpicture}
% % \\
% % \begin{tikzpicture}
% %     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
% %     \tikzstyle{e}=[]

% %     \node[v] (v1) at ( 0, 0) {kxyz};
% %     \node[v] (v2) at (-1,-1) {kxy};
% %     \node[v] (v3) at (-2,-2) {kx};
% %     \node[v] (v4) at (-3,-3) {k};
% %     \node[v] (v5) at ( 1,-1) {z plan};
% %     \node[v] (v6) at ( 0,-2) {y plan};
% %     \node[v] (v7) at (-1,-3) {x plan};
% %     \node[v] (v8) at (-2,-4) {k plan};

% %     \tedge{v1}{v2}{solid}{}{};
% %     \tedge{v1}{v5}{solid}{}{};
% %     \tedge{v2}{v3}{solid}{}{};
% %     \tedge{v2}{v6}{solid}{}{};
% %     \tedge{v3}{v4}{solid}{}{};
% %     \tedge{v3}{v7}{solid}{}{};
% %     \tedge{v4}{v8}{solid}{}{};
% % \end{tikzpicture}

% \caption{A well-constrained graph whose nodes are subgraphs labeled with their density. Below are its 3 optimal DR-Plans (partially complete). The center vertex has weight $k$ and is well-constrained itself. The radial nodes have weights $x,y,z \neq k$ with equivalent edge weights, making any union between $k$ and the others well-constrained. \todo{Make this figure more clear.}}
% \label{3-plans}
% \end{figure*}

In the problem of the optimal DR-Plan there is generally not a unique plan. For example, a graph that is formed by the union of 3 well-constrained subgraphs that all intersect on a well-constrained subgraph has ${3\choose 2} = 3$ unique optimal DR-Plans; any two of these subgraphs will suffice as children.
% Indeed, we will prove a union of $N$ well-constrained subgraphs will result in $N$ unique plans, but that at the $N^{\text{th}}$ level of the tree it will always be the same. Therefore, all choices of decomposition are in some sense equivalent. The theorem we seek to prove is thus:
However, we will show that regardless of which children are chosen for the plan, the recombination will require solving of the same systems. Thus, this definition of an optimal DR-plan could be considered the canonical DR-plan. To assist in showing this, we prove this core theorem throughout this section:

\begin{theorem}\label{theorem:main}
Given a well-constrained 2-dimensional bar-joint graph $G$, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\end{theorem}

% \begin{proof}
% Immediate from Lemma \ref{lemma:main_trivial} and \ref{lemma:main_wellconstrained}.
% \end{proof}

% \begin{lemma}\label{lemma:main_trivial}
% In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial, then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
% \end{lemma}

% \begin{lemma}\label{lemma:main_wellconstrained}
% In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained, then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% \end{lemma}

@@

\begin{lemma}\label{lemma:union_intersection}
If $F_i$ and $F_j$ are well-constrained subgraphs of the same well-constrained graph $F$, then it must be that:
\begin{enumerate}
    \item $F_i\cup F_j$ is not trivial.
    \item $F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial.
    \item $F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained.
    \item $F_i\cap F_j$ is not under-constrained.
\end{enumerate}
\end{lemma}

@@

% For the following lemmas, we define $F_i$ and $F_j$ as well-constrained subgraphs of the same well-constrained graph $F$.
% We wish to prove the following bijections:

% \begin{center}
% \begin{tabular}{|c|c|}
% \hline
% \textbf{Union is\ldots} & \textbf{Intersection is\ldots} \\ \hline
% \sout{trivial}          & --- \\ \hline
% under-constrained       & trivial \\ \hline
% well-constrained        & well-constrained \\ \hline
% ---                     & \sout{under-constrained} \\ \hline
% \end{tabular}
% \end{center}

% \begin{lemma}\label{t-l1}
% $F_i\cup F_j$ cannot be trivial.
% \end{lemma}

% \begin{proof}
% Follows from the definition of a trivial graph. It would imply that the well-constrained graphs were also trivial since they would be subgraphs of a trivial graph.
% \end{proof}

% \begin{lemma}\label{uc-l1}
% $F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial.
% \end{lemma}

% \begin{proof}
% It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction, we have that $d(F_i\cup F_j)=l<k$. If it were equal to $k$ it would be well-constrained since, as a subgraph of $F$, it satisfies the other properties of a well-constrained graph; if it were greater than $k$ then it would be over-constrained. Therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=2k-l>k$. The only way to have an over-constrained subgraph in a well-constrained graph is if it is trivial.

% In the reverse direction, we know that $d(F_i\cap F_j)>k$ because it is trivial. Thus, by the same math, it is clear that $d(F_i\cup F_j)<k$ and it must be under-constrained.
% \end{proof}

% \begin{lemma}\label{wc-l1}
% $F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained.
% \end{lemma}

% \begin{proof}
% It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction we have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=k$. Since $F_i\cap F_j$ is a subgraph of $F$, which is well-constrained, it is also well-constrained.

% In the reverse direction the same math proves that $d(F_i\cup F_j)=k$ and, since it is also a subgraph of $F$, it too is well-constrained.
% \end{proof}

% \begin{lemma}\label{iuc-l1}
% $F_i\cap F_j$ cannot be under-constrained.
% \end{lemma}

% \begin{proof}
% Subgraphs of well-constrained graph $F$ can only be trivial, under-constrained, or well-constrained. So it follows from Lemmas \ref{t-l1}, \ref{uc-l1}, and \ref{wc-l1} that only trivial and well-constrained intersections are possible.
% \end{proof}

@@

At this point we limit our discussion to the scope of 2D graphs. All vertex weights are $2$, all edge weights are $1$, and constant $k= -{{3}\choose{2}}=-3$. Trivial graphs are a single vertex and empty set. Furthermore, 2D well-constrained graphs must be connected.
% The greatest density of a 2D well-constrained graph is $-2$ (the vertex). The other disconnected part of the graph would need to have a density of $-1$, which is over-constrained and not possible in a well-constrained graph (because there is no trivial graph with that density).

@@

\subsubsection{Proving the Main Theorem \ref{theorem:main}}
\label{sec:maintheorem}
Lemmas \ref{lemma:wc_intersection_makes_all_wc} and \ref{lemma:uc_intersection_makes_all_uc} show that $CompleteDRP(C)$ will result in one of two scenarios. (A) Either all $C_1,\ldots,C_N$ intersect trivially and all of them must be unioned to make $C$, or (B) all $C_1,\ldots,C_N$ intersect on some common well-constrained subgraph and any two union to make $C$.

% \begin{figure}\centering
% \begin{tikzpicture}
%     \draw[rotate=0]  (0,0) ellipse (1.5cm and .3cm);
%     \draw[rotate around={-59:(.7,1.2)}] (.8,1.1) ellipse (1.5cm and .3cm);
%     \draw[rotate around={59:(-.7,1.2)}] (-.8,1.1) ellipse (1.5cm and .3cm);

%     % \draw[rotate around={59:(.7,-1.2)}] (.8,-1.1) ellipse (1.5cm and .3cm);
%     % \draw[rotate around={-59:(-.7,-1.2)}] (-.8,-1.1) ellipse (1.5cm and .3cm);

%     % \draw[rotate=0] (1,1) ellipse (.1cm and .1cm);
%     % \draw[rotate=66] (0,0) ellipse (.1cm and .1cm);
% \end{tikzpicture}
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{el}=[draw, ellipse, minimum height=.75cm, minimum width=1.5cm]
%     \tikzstyle{e}=[]

%     \node[el] (m) at (0,    0) {k};
%     \node[v]  (l) at (-1.5, 0) {b};
%     \node[v]  (r) at (1.5,  0) {c};

%     \node[el] (tl) at (-1,  1) {i};
%     \node[el] (tr) at (1,   1) {j};
%     \node[v]  (t)  at (0,   2) {a};

%     % \node[el] (bl) at (-1,  -1) {l};
%     % \node[el] (br) at (1,   -1) {m};
%     % \node[v]  (b)  at (0,   -2) {d};

%     % \node[el] (v2) at (-1,-1) {b};
%     % \node[el] (v3) at (-1,-1) {b};
%     % \node[el] (v4) at (-1,-1) {b};
%     % \node[el] (v5) at (-1,-1) {b};

%     \tedge{m}{l}{solid}{}{};
%     \tedge{m}{r}{solid}{}{};

%     \tedge{l}{tl}{solid}{}{};
%     \tedge{tl}{t}{solid}{}{};
%     \tedge{r}{tr}{solid}{}{};
%     \tedge{tr}{t}{solid}{}{};

%     % \tedge{l}{bl}{solid}{}{};
%     % \tedge{bl}{b}{solid}{}{};
%     % \tedge{r}{br}{solid}{}{};
%     % \tedge{br}{b}{solid}{}{};
% \end{tikzpicture}

% \caption{Each node contains a subgraph of the entire, well-constrained graph $G$. We take $Idc(G,a\cup i\cup b)$, $Idc(G,a\cup j\cup c)$, and $Idc(G,b\cup k\cup c)$ to be well-constrained. If the union of any two of these listed unions is under-constrained then it immediately follows that all such unions are under-constrained and that nodes $a,b,c$ must all be trivial subgraphs.
% % Each node contains a subgraph of the entire, well-constrained graph. We take $a\cup i\cup b$, $a\cup j\cup c$, $b\cup k\cup c$, $b\cup l\cup d$, and $c\cup m\cup d$ to be well-constrained. If the union of any two of these listed unions is under-constrained then it immediately follows that all such unions are under-constrained and that nodes $a,b,c,d$ must all be trivial subgraphs.
% % THIS IS NOT TECHNICALLY CORRECT... $a\cup i\cup b$ doesn't include the edge between them... Is there a better way to phrase this?
% }
% \label{trivial-intersection}
% \end{figure}

\begin{theorem}\label{theorem:main_wellconstrained}
In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial, then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
\end{theorem}

% \begin{proof}
% From Lemma \ref{uc-l1}, if it is trivial then $C_i \cup C_j$ must be under-constrained. If it is under-constrained, it must be part of some larger well-constrained subgraph $D$. If $D$ is not $C$ itself, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.
%  % For $C$ to be well-constrained... WHAT????

% If there was some $X\subset [1,\ldots,N]$ such that $\bigcup_{i\in X}{C_i}\neq C$ but it was well-constrained, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.

% This means that in the case of a trivial intersection, all of the children come together to form some complex structure that is itself rigid. Such an example is shown in Figure \ref{trivial-intersection}.
% \end{proof}

\begin{proof}
Take $X\subset \{1,\ldots,N\}$ and $D=\bigcup_{i\in X}{C_i}$. If $D\neq C$ but it was well-constrained, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.

\todo{Uses 2D requirement:}
If $D= C$, then we contradict the assumption that $C_i \cap C_j$ is trivial. By Lemma \ref{lemma:uc_intersection_makes_all_uc}, if $C_i \cap C_j$ is trivial then for $k\notin X$, $D\cap C_k$ must be one or more trivial subgraphs. Furthermore, by definition of a DR-plan, $C_k=C\cap C_k=D\cap C_k$. Together, this shows that $C_k$ cannot be well-constrained, violating the properties of a DR-plan.
\end{proof}

% As such, there must be additional vertex-maximal proper subgraphs, all of whose intersections with one another are trivial subgraphs or $\emptyset$. All of these subgraphs form a complex structure that is well-constrained and must be the parent itself (otherwise we did not have vertex-maximal subgraphs to begin with).

\begin{theorem}\label{theorem:main_trivial}
In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained, then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% Namely, these children are any 2 of its well-constrained vertex-maximal proper subgraphs.
\end{theorem}

\begin{proof}
In a valid DR-plan, all children must be proper subgraphs. Therefore, for the union to be the parent (and satisfy the conditions of a DR-plan) there must be at least two children. It follows directly from Lemma \ref{lemma:wc_intersection_makes_all_wc} that if there exists $C_i, C_j$ such that $C_i \cup C_j$ is well-constrained, then the smallest fan-in at this node can be made by selecting any two $C_i, C_j$.
% you found a tree with only 2 children.
% Clearly, this is the optimal choice at this level.
However, for it to be a solution to $OptimalDRP(G)$, it must not affect the maximum fan-in for any descendant.

Take $D=\bigcap_{k=1}^N{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $m\neq n$. This continues for $N-1$ levels total, always with fan-in of two, at which point every descendant of $C$ is some $Idc(C,D\cup R_k)$.
\end{proof}

% This is demonstrated with $N=3$ in Figure \ref{3-plans}. It is clear that until this point, the fan-in at every node is exactly 2 in the optimal solution. This follows from the discussion above. Now, at this level, the fan-in must be equal in all scenarios. In fact, at node $k$ it will be 1 (because of $D$ which is well-constrained) plus whatever fan-in $R_k$ incurs.

With these two proofs, the original Theorem \ref{theorem:main} has been proven. With this we have formulated the notion of a canonical DR-plan.
% Any optimal DR-plan of a well-constrained graph must follow this pattern.
No matter which two children you choose in case (A) all children must always be included; in case (B), the recombination steps will always involve the same systems.

@@

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}
  \centering
  \begin{tikzpicture}[scale=2]
        \tikzstyle{v}=[draw, circle, minimum size=0.1cm, font=\footnotesize]
        \tikzstyle{e}=[]

        \node[v] (v1) at (0,0.866) {$a_1$};
        \node[v] (v2) at (-1,-0.866) {$a_2$};
        \node[v] (v3) at (1,-0.866) {$a_3$};

        \node[v] (v4) at (0,0.577-.1) {$b_1$};
        \node[v] (v5) at (-0.667,-0.577-.1) {$b_2$};
        \node[v] (v6) at (0.667,-0.577-.1) {$b_3$};

        \node[v] (v7) at (0,0.289-.2) {$c_1$};
        \node[v] (v8) at (-0.333,-0.289-.2) {$c_2$};
        \node[v] (v9) at (0.333,-0.289-.2) {$c_3$};

@@

    \caption{}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}
    \centering
    \begin{tikzpicture}[scale=.9, transform shape]
        \tikzstyle{v}=[draw, circle, minimum size=0.75cm, font=\footnotesize]
        \tikzstyle{e}=[]

        \node (c0) at (0,0) {$\{a_1,a_2,a_3,b_1,b_2,b_3,c_1,c_2,c_3\}$};
        \node (c1a) at (-2,-1) {$\{a_1,a_2,a_3,b_1,b_2,b_3\}$};
        \node (c1b) at (2,-1) {$\{b_1,b_2,b_3,c_1,c_2,c_3\}$};
        \node (c2a) at (-2,-2) {$\{a_1,a_2,a_3\}$};
        \node (c2b) at (0,-2) {$\{b_1,b_2,b_3\}$};
        \node (c2c) at (2,-2) {$\{c_1,c_2,c_3\}$};
        \node (c2ab1) at (-5.6,-2) {$\{a_1,b_1\}$};
        \node (c2ab2) at (-4.5,-2) {$\{a_2,b_2\}$};
        \node (c2ab3) at (-3.4,-2) {$\{a_3,b_3\}$};
        \node (c2bc1) at (5.6,-2) {$\{b_1,c_1\}$};
        \node (c2bc2) at (4.5,-2) {$\{b_2,c_2\}$};
        \node (c2bc3) at (3.4,-2) {$\{b_3,c_3\}$};

@@

\begin{figure*}\centering
\begin{tikzpicture}[scale=3]
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (0,0.866) {$a_1$};
    \node[v] (v2) at (-1,-0.866) {$a_2$};
    \node[v] (v3) at (1,-0.866) {$a_3$};

    \node[v] (v4) at (0,0.433-.125) {$b_1$};
    \node[v] (v5) at (-0.5,-0.433-.125) {$b_2$};
    \node[v] (v6) at (0.5,-0.433-.125) {$b_3$};

@@

@@

    \coordinate (ib0) at (-0.167,-0.433-.125-0.1);
    \coordinate (ib1) at (0.167,-0.433-.125-0.1);
    \coordinate (ib2) at (-0.167,-0.433-.125+0.1);
    \coordinate (ib3) at (0.167,-0.433-.125+0.1);
    \draw (v5) -- (ib0) -- (ib1) -- (v6);
    \draw (v5) -- (ib2) -- (ib3) -- (v6);
    \draw (ib0) -- (ib3);
    \draw (ib2) -- (ib1);

    % \draw[rotate around={60:(-1,-0.866)}] (v2) -- (-0.333,-0.766) -- (0.333,-0.766) -- (v1);
    % \draw (v2) -- (ob2) -- (ob3) -- (v1);
    % \draw (ob0) -- (ob3);
    % \draw (ob2) -- (ob1);
% \newcommand{\tedge}[5]{\draw[#3] (#1)-- node[e, #5] (e#4) {#4} (#2)}

>>>>

\newcommand{\usestwod}{\todo{Uses 2D requirement:}}
\renewcommand{\usestwod}{}

@@

In the problem of the optimal DR-Plan there is generally not a unique plan.
% Indeed, we will prove a union of $N$ well-constrained subgraphs will result in $N$ unique plans, but that at the $N^{\text{th}}$ level of the tree it will always be the same. Therefore, all choices of decomposition are in some sense equivalent. The theorem we seek to prove is thus:
However, we will show that regardless of which children are chosen for the plan, so long as they satisfy the definition of an optimal DR-plan, the recombination will require solving of the same systems. Being the smallest such structure that offers this, the definition of an optimal DR-plan could be considered the canonical DR-plan.
% To assist in showing this, we prove this core theorem throughout this section:

In this section, we discuss 2D bar-joint graphs. All vertex weights are $2$, all edge weights are $1$, and constant $k= -{{3}\choose{2}}=-3$. Trivial graphs are a single vertex and empty set. Furthermore, 2D well-constrained graphs must be connected.
% The greatest density of a 2D well-constrained graph is $-2$ (the vertex). The other disconnected part of the graph would need to have a density of $-1$, which is over-constrained and not possible in a well-constrained graph (because there is no trivial graph with that density).

\begin{theorem}\label{theorem:main}
Given a well-constrained 2-dimensional bar-joint graph $G$, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
This covers all potential cases.
\end{theorem}

\begin{proof}
Remark \ref{lemma:union_intersection} shows that the intersection of any two well-constrained subgraphs (such as $C_i$ and $C_j$) can only result in trivial or well-constrained subgraphs. Therefore, these are the only possibilities to consider.

\begin{enumerate}
\item
% In a valid DR-plan, all children must be proper subgraphs. Therefore, for the union to be the parent (and satisfy the conditions of a DR-plan) there must be at least two children.
It follows directly from Lemma \ref{lemma:wc_intersection_makes_all_wc} that if there exists $C_i, C_j$ such that $C_i \cup C_j$ is well-constrained, then the smallest fan-in at this node can be made by selecting any two $C_i, C_j$.
% you found a tree with only 2 children.
% Clearly, this is the optimal choice at this level.
However, for it to be a solution to $OptimalDRP(G)$, it must not affect the maximum fan-in for any descendant.

Take $D=\bigcap_{k\in N}{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $m\neq n$. This continues for $N-1$ levels total, always with fan-in of two (the minimum possible), at which point every descendant of $C$ is some $Idc(C,D\cup R_k)$.

%%%%%%%%%%%%%%%

\item
Take $X\subset \{1,\ldots,N\}$ and $D=\bigcup_{i\in X}{C_i}$. If $D\neq C$ but it was well-constrained, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.

\usestwod
By Lemma \ref{lemma:uc_intersection_makes_all_uc}, if $C_i \cap C_j$ is trivial then for $k\notin X$, $D\cap C_k$ must be one or more trivial subgraphs. Since $C_k=C\cap C_k=D\cap C_k$, by definition of a DR-plan, the assumption that $C_k$ is well-constrained has been contradicted. Thus, $X$ must be all of $\{1,\ldots,N\}$.
\end{enumerate}
\end{proof}

The following subsections provide the supporting proofs.

@@

% This is general, not for 2d
\begin{remark}\label{lemma:union_intersection}
If $F_i$ and $F_j$ are well-constrained subgraphs of the same well-constrained graph $F$, then it must be that:
\begin{enumerate}
    \item $F_i\cup F_j$ is not trivial.
    \item $F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial.
    \item $F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained.
    \item $F_i\cap F_j$ is not under-constrained.
\end{enumerate}
\end{remark}

@@

@@

@@

@@

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}\centering
  \begin{tikzpicture}[scale=2]
        \tikzstyle{v}=[draw, circle, minimum size=0.1cm, font=\footnotesize]
        \tikzstyle{c}=[draw, circle, inner sep=1.5, fill=black]
        \tikzstyle{e}=[]

        \node[c] (v1) at (0,0.866) [label={left,inner sep=.555}:$a_1$]{};
        \node[c] (v2) at (-1,-0.866) [label={below,inner sep=.555}:$a_2$]{};
        \node[c] (v3) at (1,-0.866) [label={above,inner sep=.555}:$a_3$]{};

        \node[c] (v4) at (0,0.577-.1) [label={left,inner sep=.555}:$b_1$]{};
        \node[c] (v5) at (-0.667,-0.577-.1) [label={below,inner sep=.555}:$b_2$]{};
        \node[c] (v6) at (0.667,-0.577-.1) [label={above,inner sep=.555}:$b_3$]{};

        \node[c] (v7) at (0,0.289-.2) [label={left,inner sep=.555}:$c_1$]{};
        \node[c] (v8) at (-0.333,-0.289-.2) [label={below,inner sep=.555}:$c_2$]{};
        \node[c] (v9) at (0.333,-0.289-.2) [label={above,inner sep=.555}:$c_3$]{};

@@

    \caption{}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}\centering
    \begin{tikzpicture}[scale=.9, transform shape]
        \tikzstyle{v}=[draw, circle, minimum size=0.75cm, font=\footnotesize]
        % \tikzstyle{b}=[draw, font=\footnotesize]
        \tikzstyle{b}=[]
        \tikzstyle{e}=[]

        \node[b] (c0) at (0,0) {$\{a_1,a_2,a_3,b_1,b_2,b_3,c_1,c_2,c_3\}$};
        \node[b] (c1a) at (-2,-1) {$\{a_1,a_2,a_3,b_1,b_2,b_3\}$};
        \node[b] (c1b) at (2,-1) {$\{b_1,b_2,b_3,c_1,c_2,c_3\}$};
        \node[b] (c2a) at (-2,-2) {$\{a_1,a_2,a_3\}$};
        \node[b] (c2b) at (0,-2) {$\{b_1,b_2,b_3\}$};
        \node[b] (c2c) at (2,-2) {$\{c_1,c_2,c_3\}$};
        \node[b] (c2ab1) at (-5.6,-2) {$\{a_1,b_1\}$};
        \node[b] (c2ab2) at (-4.5,-2) {$\{a_2,b_2\}$};
        \node[b] (c2ab3) at (-3.4,-2) {$\{a_3,b_3\}$};
        \node[b] (c2bc1) at (5.6,-2) {$\{b_1,c_1\}$};
        \node[b] (c2bc2) at (4.5,-2) {$\{b_2,c_2\}$};
        \node[b] (c2bc3) at (3.4,-2) {$\{b_3,c_3\}$};

@@

\begin{figure*}\centering
\begin{tikzpicture}[scale=3]
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{c}=[draw, circle, inner sep=1.5, fill=black]
    \tikzstyle{e}=[]

    \node[circle,fill=white,inner sep=7] (center) at (0,0-.125-.1) {};

    \node[c] (v1) at (0,0.866) [label={left,inner sep=.555}:$a_1$]{};
    \node[c] (v2) at (-1,-0.866) [label={below,inner sep=.555}:$a_2$]{};
    \node[c] (v3) at (1,-0.866) [label={above,inner sep=.555}:$a_3$]{};

    \node[c] (v4) at (0,0.433-.125) [label={left,inner sep=.555}:$b_1$]{};
    \node[c] (v5) at (-0.5,-0.433-.125) [label={below,inner sep=.555}:$b_2$]{};
    \node[c] (v6) at (0.5,-0.433-.125) [label={above,inner sep=.555}:$b_3$]{};

@@

    \tedge{v4}{center}{dashed}{}{};
    \tedge{v5}{center}{dashed}{}{};
    \tedge{v6}{center}{dashed}{}{};

@@

    \draw[rotate around={60:(-1,-0.866)}] (v2) -- (-0.333,-0.766) -- (0.333,-0.766) -- (v1);
    \draw[rotate around={60:(-1,-0.866)}]  (v2) -- (-0.333,-0.966) -- (0.333,-0.966) -- (v1);
    \draw[rotate around={60:(-1,-0.866)}]  (-0.333,-0.766) -- (0.333,-0.966);
    \draw[rotate around={60:(-1,-0.866)}]  (-0.333,-0.966) -- (0.333,-0.766);

    \draw[rotate around={-60:(1,-0.866)}] (v3) -- (0.333,-0.766) -- (-0.333,-0.766) -- (v1);
    \draw[rotate around={-60:(1,-0.866)}]  (v3) -- (0.333,-0.966) -- (-0.333,-0.966) -- (v1);
    \draw[rotate around={-60:(1,-0.866)}]  (-0.333,-0.766) -- (0.333,-0.966);
    \draw[rotate around={-60:(1,-0.866)}]  (-0.333,-0.966) -- (0.333,-0.766);

    \coordinate (ib0) at (-0.167,-0.433-.125-0.1); %(-.167,-.658)
    \coordinate (ib1) at (0.167,-0.433-.125-0.1); %(.167,-.658)
    \coordinate (ib2) at (-0.167,-0.433-.125+0.1);%(-.167,-.458)
    \coordinate (ib3) at (0.167,-0.433-.125+0.1);%(.167,-.458)
    \draw (v5) -- (ib0) -- (ib1) -- (v6);
    \draw (v5) -- (ib2) -- (ib3) -- (v6);
    \draw (ib0) -- (ib3);
    \draw (ib2) -- (ib1);

    \draw[rotate around={60:(-0.5,-0.558)}] (v5) -- (-.167,-.658) -- (.167,-.658) -- (v4);
    \draw[rotate around={60:(-0.5,-0.558)}]  (v5) -- (-.167,-.458) -- (.167,-.458) -- (v4);
    \draw[rotate around={60:(-0.5,-0.558)}]  (-.167,-.658) -- (.167,-.458);
    \draw[rotate around={60:(-0.5,-0.558)}]  (-.167,-.458) -- (.167,-.658);

    \draw[rotate around={-60:(0.5,-0.558)}] (v6) -- (.167,-.658) -- (-.167,-.658) -- (v4);
    \draw[rotate around={-60:(0.5,-0.558)}]  (v6) -- (.167,-.458) -- (-.167,-.458) -- (v4);
    \draw[rotate around={-60:(0.5,-0.558)}]  (-.167,-.658) -- (.167,-.458);
    \draw[rotate around={-60:(0.5,-0.558)}]  (-.167,-.458) -- (.167,-.658);
% \newcommand{\tedge}[5]{\draw[#3] (#1)-- node[e, #5] (e#4) {#4} (#2)}
